### 2018-04-06 reports/thesis/chapters/5_inference.tex
Made script for inference example, changed labelling in inference chapter.

Model misspecification appears to be the main source of error. The $z$ statistics can be inspected using a histogram, as shown in Figure \ref{fig:z_histo}. The histogram of the $z$ statistics do not look Normal which seems to suggest that the assumption of $z_{i,j}\sim \normal(0,1)$ is incorrect. However this assumption can relaxed and can be done using the empirical null \citep{efron2004large}.

@@

\begin{figure}
    \centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
    	\includegraphics[width=\textwidth]{../figures/inference/z_histo.eps}
    \end{subfigure}
	\begin{subfigure}[b]{0.49\textwidth}
    	\includegraphics[width=\textwidth]{../figures/inference/z_qq.eps}
    \end{subfigure}
	}
    \caption{Histogram of the $z$ statistics}
    \label{fig:z_histo}
\end{figure}

>>>>

Model misspecification appears to be the main source of error. The $z$ statistics can be inspected using a histogram or a QQ plot, as shown in Figure \ref{fig:z_histo}. It can be seen that the $z$ statistics do not look Normal which seems to suggest that the assumption of $z_{i,j}\sim \normal(0,1)$ is incorrect. However this assumption can relaxed and can be done using the empirical null \citep{efron2004large}.

@@

\begin{figure}
    \centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
    	\includegraphics[width=\textwidth]{../figures/inference/z_histo.eps}
    	\caption{Histogram}
    \end{subfigure}
	\begin{subfigure}[b]{0.49\textwidth}
    	\includegraphics[width=\textwidth]{../figures/inference/z_qq.eps}
    	\caption{QQ plot}
    \end{subfigure}
	}
    \caption{Distribution of the  $z$ statistics with the BH procedure critical region}
    \label{fig:z_histo}
\end{figure}
